%%
This chapter introduces the context and generalities relative to the work.



%====================================================================================================
% Context
%====================================================================================================
\section{Context}
This bachelor's thesis was carried out to support the research of the institute \Gls{IRSOL}. \newline
<<\Gls{IRSOL} is a research institute dependent on a foundation of the same name and affiliated to Università della Svizzera italiana.>>$^1$
The institute is based above Locarno in Ticino. \newline
Their research is mainly based on the measurement and characterization of the sun, and specializes in :
<<
\begin{enumerate}
    \item observational spectropolarimetry and instrument development,
    \item theoretical modeling of the generation and transfer of polarized radiation,
    \item numerical simulation of the solar atmosphere and numerical radiative transfer.
\end{enumerate}>>\footnote{\cite{IRSOL_research} IRSOL, 2023. RESEARCH ACTIVITY, Research Activity at IRSOL. [Online]. [Accessed on 21.07.2023]. Available at: https://www.irsol.usi.ch/research/research-activity/}

The problem is that the institute is looking to expand its equipment in order to develop their research.
However, it is necessary to know the limitations of the measuring instruments, as well as the quality of the observation site.
Their first development objective would be to integrate an adaptive optics system \acrfull{ao}.
\newline
In odrer to asses the usefullness of adaptative optics two Bachelor thesis are conducted.
\begin{enumerate}
    \item (Celui de DOM)
    \item This thesis : "Analyseur de la turbulence optique pour le télescope solaire IRSOL" (Optical turbulence analyser for \Gls{IRSOL}'s solar telescope)
\end{enumerate}
The 1\textsuperscript{st} one is meant to measure the optical imperfections of the telescope itself and maybe of other optical equipment.
The 2\textsuperscript{nd} one aims to analyse optical turbulence on site.

Once these two projects are completed, IRSOL will be able to determine whether the acquisition of an \acrfull{ao} makes sense
and they will also be able to quantify the limiting element to their research (the observation site or the telescope).



%====================================================================================================
% Issue at hand
%====================================================================================================
\section{Issue at hand}
In a discussion with the institute, it was said: "Seeing evolves over the course of the day.
When the sun rises, the ground warms up and the heat rises. This is when seeing is at its worst.
But when the sun goes down, there's a moment when seeing is almost non-existent because the air currents freeze before going down again."
\bigbreak
The issue at hand is that the quality of the observation site is known but cannot be quantified.
The aim of this study is to quantify the quality of their observation site.
The instrument used will be the DIMM \textbf{\textcolor{red}{RAJOUTER GLOSSAIRE DIMM}} (Differential image motion monitor).

A DIMM \textbf{\textcolor{red}{RAJOUTER GLOSSAIRE DIMM}} works as follows (simplified version) :
\begin{enumerate}
    \item Capture an image masked by two small holes.
    \item Tracking the movement of these images.
    \item Measurement of the standard deviation of this movement.
    \item Conversion of previous result into turbulent layer thickness.
\end{enumerate}
The aim will be to play with the exposure time to determine the location of the image center, but also to freeze the turbulence.
\bigbreak
The issue at hand is that the the teslescope has some unkown optical imperfecitons. This study aims to measure them.

The short methodology explanation is as follows:
\begin{enumerate}
    \item Sets of 2 pictures are taken (1 focused, 1 unfocused (in a known way))
    \item The best sets are kept and stacked.
    \item The stack is run throug a code which output will then be interpreted to find the imperfections.
\end{enumerate}

If the exposure time is short enough, turbulences will eventually be fixed into place, resulting in a sharp image.\footnote{\cite{Law_lucky} Law, 2006. Lucky imaging: High angular resolution imaging in the visible from the ground. in: Astronomy \& Astrophysics [online], February 2006, N°446, pp. 739-745. ISSN
1950-6295. [Accessed on 24.02.2023]. Available at: https://www.aanda.org/articles/aa/abs/2006/05/} Furthermore, if the time between a set of 2 pictures is short enough, the perturbation will not have moved which means a set has the same perturbations for both pictures.

In a perfect world, the exposures time is infinitely small and the time inbetween two frames inexistent. This will be further discussed.
The process of stacking images is called lucky imaging. The theory behind it it that the mean turbulence is null\footnote{\cite{JOLISSAINT_master} JOLISSAINT, Laurent, 1996. XXXXX. Genève : XXXX. Master's thesis}, thus the result should be a picture free of aberations caused by the atmosphere.

Alternatively, long exposure times will also cancel the effect of atmospheric turbulence.

The long explanation is the subject of this document.

